AVERAGE STATES ARIMAX MODEL - without log-back transformations

### 2025-06-23 models_with_logback/ES_AVERAGE/AVERAGE.Rmd
reviewed comments

---
title: "AVERAGE STATES ARIMAX MODEL - Influenza hospitalization data"
author: "Victor Felix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---

This function utilizes ensembles and single automatic ARIMAX models which have mean hospitalization on U.S. states as exogenous variables. The function fits on a rolling window of previous 104 weeks for the state under analysis and a rolling windows with the same size with 1 week-lag for the exogenous variables to generate forecasts. It return some metrics that evaluate the performance of the mod
els:target_end_date, abs_error, cases, forecast, 'N_of_models", weighted interval score (WIS), predictive quantiles. The user can choose a  single best automatic ARIMAXs (auto=TRUE), or ensembles of 27 permutations of 0,1,2 pdq's (ES27=TRUE) or 64 permutations of 0,1,2,3 pdq's (ES64=TRUE). The user also chooses the number of weeks ahead for each forecast, and the size of the rolling window which is set as 2 years (104 weeks).

>>>>

---
title: "AVERAGE STATES ARIMAX MODEL - with log-back transformations"
author: "Victor Felix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---

Here we run ensembles and single automatic ARIMAX models for forecasting weekly hospitalizations in 48 states on the contiguous U.S. These model use mean hospitalization across the U.S. states as exogenous variables. The function fits on a rolling window of previous 104 weeks for the state under analysis and a rolling windows with the same size with 1 week-lag for the exogenous variables to generate forecasts. These models include log-back transformations. It return some metrics that evaluate the performance of the models:target_end_date, abs_error, cases, forecast, 'N_of_models", weighted interval score (WIS), predictive quantiles. The user can choose a  single best automatic ARIMAXs (auto=TRUE), or ensembles of 27 permutations of 0,1,2 pdq's (ES27=TRUE) or 64 permutations of 0,1,2,3 pdq's (ES64=TRUE). The user also chooses the number of weeks ahead for each forecast, and the size of the rolling window which is set as 2 years (104 weeks).

### 2025-06-23 models_without_logback/ES_AVERAGE/AVERAGE.Rmd
reviewed comments

---
title: "AVERAGE STATES ARIMAX MODEL - with log-back transformations"
author: "Victor Felix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---

Here we run ensembles and single automatic ARIMAX models for forecasting weekly hospitalizations in 48 states on the contiguous U.S. These model use mean hospitalization across the U.S. states as exogenous variables. The function fits on a rolling window of previous 104 weeks for the state under analysis and a rolling windows with the same size with 1 week-lag for the exogenous variables to generate forecasts. These models include log-back transformations. It return some metrics that evaluate the performance of the models:target_end_date, abs_error, cases, forecast, 'N_of_models", weighted interval score (WIS), predictive quantiles. The user can choose a  single best automatic ARIMAXs (auto=TRUE), or ensembles of 27 permutations of 0,1,2 pdq's (ES27=TRUE) or 64 permutations of 0,1,2,3 pdq's (ES64=TRUE). The user also chooses the number of weeks ahead for each forecast, and the size of the rolling window which is set as 2 years (104 weeks).

@@

# Loads the AVERAGE states models
source("ES_AVERAGE_48.R", local = TRUE, chdir = TRUE)

@@

```{r}
save.image("AVERAGE_MODELS_influenza_hospitalization.Rdata")
```

>>>>

---
title: "AVERAGE STATES ARIMAX MODEL - without log-back transformations"
author: "Victor Felix"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---

Here we run ensembles and single automatic ARIMAX models for forecasting weekly hospitalizations in 48 states on the contiguous U.S. These model use mean hospitalization across the U.S. states as exogenous variables. The function fits on a rolling window of previous 104 weeks for the state under analysis and a rolling windows with the same size with 1 week-lag for the exogenous variables to generate forecasts. These models do not include log-back transformations. It return some metrics that evaluate the performance of the models:target_end_date, abs_error, cases, forecast, 'N_of_models", weighted interval score (WIS), predictive quantiles. The user can choose a  single best automatic ARIMAXs (auto=TRUE), or ensembles of 27 permutations of 0,1,2 pdq's (ES27=TRUE) or 64 permutations of 0,1,2,3 pdq's (ES64=TRUE). The user also chooses the number of weeks ahead for each forecast, and the size of the rolling window which is set as 2 years (104 weeks).

@@

# Loads the AVERAGE states models
source("ES_AVERAGE_48_nolog.R", local = TRUE, chdir = TRUE)

@@

```{r}
save.image("AVERAGE_MODELS_influenza_hospitalization_nolog.Rdata")
```
